% \clearpage
% \printglossaries


%   NdYAG1064


\newglossaryentry{Molecular descriptor}
{
    name=Molecular descriptor,
    description={The main classes of theoretical molecular descriptors are: 1) 0D-descriptors (i.e. constitutional descriptors, count descriptors), 2) 1D-descriptors (i.e. list of structural fragments, fingerprints),3) 2D-descriptors (i.e. graph invariants),4) 3D-descriptors (such as, for example, 3D-MoRSE descriptors, WHIM descriptors, GETAWAY descriptors, quantum-chemical descriptors, size, steric, surface and volume descriptors),5) 4D-descriptors (such as those derived from GRID or CoMFA methods, Volsurf}
}



\newglossaryentry{Kernel functions}
{
    name=Kernel functions,
    description={核函数的作用就是隐含着一个从低维空间到高维空间的映射，而这个映射可以把低维空间中线性不可分的两类点变成线性可分的。当然，我举的这个具体例子强烈地依赖于数据在原始空间中的位置。事实中使用的核函数往往比这个例子复杂得多。它们对应的映射并不一定能够显式地表达出来；它们映射到的高维空间的维数也比我举的例子（三维）高得多，甚至是无穷维的。这样，就可以期待原来并不线性可分的两类点变成线性可分的了 }
}

\newglossaryentry{Binding modes}
{
    name=Binding modes,
    description={The orientation of the ligand relative to the receptor as well as the conformation of the ligand and receptor when bound to each other.}
}


\newglossaryentry{Binding Affinity calculation}
{
    name=Binding Affinity,
    description={Kd is the equilibrium dissociation constant. Its the inverse of association constant.
    Ki is inhibition constant.
    IC50 is basically 50\% of the maximum.
    Formula:
    $Ki=\frac{IC50}{(1+\frac{([L]}{Kd)}}$, Where (L) is concentration of a ligand}
}



\newglossaryentry{Decoys}
{
    name=Decoys,
    description={buried solvent-accessible surface area of the ligand upon binding}
}

% \newglossaryentry{$\Delta SAS$}
% {
%     name=$\Delta SAS$,
%     description={buried solvent-accessible surface area of the ligand upon binding}
% }



\newglossaryentry{rmsd}
{
    name=Root-mean-square deviation of atomic positions,
    description={the root-mean-square deviation of atomic positions (or simply root-mean-square deviation, RMSD) is the measure of the average distance between the atoms (usually the backbone atoms) of superimposed proteins}
}


\newglossaryentry{mol2 format}
{
    name=mol2 format,
    description={The primary advantage of using MOL2 is that it is one of the few public formats capable of supporting both a chemically-accurate description of a molecular system that contains both small organic molecules and a large number of protein or nucleic acid atoms. However, the requirement for atom type specifications has so far prevented addition of MOL2 output support into PyMOL.}
}

\newglossaryentry{steric clashes in protein structures}
{
    name=steric clashes in protein structures,
    description={Steric clashes arise due to the unnatural overlap of any two non-bonding atoms in a protein structure.}
}

\newglossaryentry{New chemical entity}
{
    name=New chemical entity,
    description={a drug that contains no active moiety that has been approved by the FDA}
}


\newglossaryentry{PDBbind-CN Database}
{
    name=PDBbind-CN Database,
    description={a comprehensive collection of the experimentally measured binding affinity data for all types of biomolecular complexes deposited in the Protein Data Bank (PDB)}
}
